Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-05-05 tex/paper1/paper1.tex
edits to the paper

\documentclass[preprint]{../aastex52/aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

\author{J. Ireland}
\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA. }
\email{jack.ireland@nasa.gov}

\author{R. T. J. McAteer}
\affil{Department of Astronomy, New Mexico State University, Las
  Cruces, NM}

\and

@@

\begin{figure}
\label{fig:loc171}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.}
\end{figure}

@@

Figures \ref{fig:compare171193} show example power spectra, plotted using
a log-log scale, from a single location inside each of the regions
shown in Figures \ref{fig:loc171} and \ref{fig:loc193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies and flattens out at higher
frequencies.

\begin{figure}
\label{fig:compare171193}
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figures \protect\ref{fig:loc171} and
  \protect\ref{fig:loc193}).  The vertical black lines indicate the 3
  and 5 minute frequencies.}
\end{figure}

@@

\begin{figure}
\label{fig:dist171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.)}
\end{figure}

\begin{figure}
\label{fig:dist193}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see Figure \ref{fig:dist171}.)}
\end{figure}

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.

\begin{figure}
\label{fig:fit171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
\caption{aaa}
\end{figure}

%\begin{figure}
%\label{fig:fit193}
%\plottwo{}{}
%\plottwo{}{}
%
%\caption{}
%\end{figure}
\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\sigma$}
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\

moss            & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\

quiet Sun       & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\

sunspot         & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\end{deluxetable}

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eq:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

Section \ref{sec:results} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the Gaussian contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and Gaussian
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

@@

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet power spectrum for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.\label{fig:comparison}}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{vaughan2010}.  Figure
\ref{fig:comparison}(b) shows that the assumption of a white-noise
background and a 95\% confidence level leads to the positive detection
of significant oscillatory power in this time series. Figure
\ref{fig:comparison}(c) shows that the assumption of a red-noise
background with the same confidence level significantly reduces the
area for which a detection may be claimed.  This simulated data, along
with the results of Section \ref{sec:results}, suggest that when
examining the wavelet transforms of time-series for wave packets, a
background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000, 2003A&A...404L...1K} and looking for alternating
brightening/darkening in those plots as a indicator of a propagating
wave.  This is essentially a coherence-based approach, as the user is
assessing the likelihood that an oscillation has been detected based
on the observed signal in multiple contiguous pixels.  However, each
pixel in these plots probably has a red-noise background power
spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
that the significance of any claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eq:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
superior description of the observed Fourier power spectrum.  This
model is consistent with previous observations by TRACE of power in
the frequency range of 1 - 10 mHz.  The moss region shows the largest
presence of this excess emission.

@@

The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
contributions from plasma at many different temperatures, heights in
the atmosphere, and many different elements \ref{}.  A deeper
understanding of the contributions from these different plasmas is
required before a good estimate of the distribution of the angle
coronal loop footpoints make with the surface can be made.

@@

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = E \frac{1}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(f) = E\frac{1}{1 + (2\pi f T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:ftexpdecay}
P_{T}(f) = \sum_{T}N(T)P_{T}(f)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energydistrib}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:energydistrib}
P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{pwrlaw} and \ref{pwrlawbump} are fit to the geometric
mean power spectra shown in Figures \ref{fig:fit171} and
\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
frequency defined by the data (Section \ref{sec:obs}).

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
regions may be approximated by a normal distribution $N(\mu, \sigma)$.
The maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:mlmean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.

The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}

@@

\bibliography{references}

\end{document}

>>>>

\documentclass[preprint2]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

\author{J. Ireland}
\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
  20771, USA.}

\author{R. T. J. McAteer}
\affil{Department of Astronomy, New Mexico State University, Las
  Cruces, NM.}

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.}
\label{fig:loc171193}
\end{figure}

@@

Figures \ref{fig:compare171193} show example power spectra, plotted using
a log-log scale, from a single location inside each of the regions
shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies and flattens out at higher
frequencies.

\begin{figure}
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
  black lines indicate the 3 and 5 minute frequencies.}
\label{fig:compare171193}
\end{figure}

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193} for the corresponding AIA 171\AA\ plots.)}
\label{fig:dist171}
\end{figure}

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist171} for the corresponding AIA 171\AA\ plots.)}
\label{fig:dist193}
\end{figure}

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 171\AA\ (shown in black).  Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).  Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}. See also Figure \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
\label{fig:fit171}
\end{figure}

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 193\AA\ (shown in black).  Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).  Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}. See also Figure \ref{fig:fit171} for the corresponding AIA 171\AA\ plots.}
\label{fig:fit193}
\end{figure}

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\sigma$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

moss            & 171\AA  & $0.47^{+0.01}_{-0.01}$  & $1.86^{+0.01}_{-0.01}$ & $-3.97^{+0.01}_{-0.00}$  & $-1.33^{+0.02}_{-0.02}$  & $1.05^{+0.03}_{-0.02}$  & $0.31^{+0.00}_{-0.01}$  \\
                & 193\AA  & $0.57^{+0.01}_{-0.01}$  & $2.09^{+0.01}_{-0.01}$ & $-4.28^{+0.00}_{-0.00}$  & $-1.97^{+0.02}_{-0.03}$  & $1.43^{+0.03}_{-0.03}$  & $0.25^{+0.00}_{-0.00}$  \\
                & & & & & & & \\

quiet Sun       & 171\AA  & $0.67^{+0.01}_{-0.01}$  & $1.73^{+0.01}_{-0.01}$ & $-2.86^{+0.00}_{-0.00}$  & $-3.49^{+0.04}_{-0.04}$  & $4.50^{+0.14}_{-0.09}$  & $0.10^{+0.01}_{-0.01}$  \\
                & 193\AA  & $0.06^{+0.01}_{-0.01}$  & $2.25^{+0.01}_{-0.01}$ & $-3.38^{+0.00}_{-0.00}$  & $-4.54^{+0.06}_{-0.10}$  & $4.72^{-0.17}_{-0.16}$  & $0.13^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

sunspot         & 171\AA  & $0.51^{+0.01}_{-0.01}$  & $2.27^{+0.02}_{-0.02}$ & $-3.79^{+0.00}_{-0.00}$  & $-2.94^{+0.02}_{-0.02}$  & $2.18^{+0.08}_{-0.07}$  & $0.29^{+0.01}_{-0.01}$  \\
                & 193\AA  & $0.02^{+0.02}_{-0.01}$  & $2.19^{+0.02}_{-0.04}$ & $-3.85^{+0.00}_{-0.00}$  & $-3.17^{+0.04}_{-0.04}$  & $1.87^{+0.11}_{-0.11}$  & $0.35^{+0.01}_{-0.01}$  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\end{deluxetable}

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

Section \ref{sec:anal} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the Gaussian contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and Gaussian
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

@@

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet power spectrum for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{2010MNRAS.402..307V}.
Figure \ref{fig:comparison}(b) shows that the assumption of a
white-noise background and a 95\% confidence level leads to the
positive detection of significant oscillatory power in this time
series. Figure \ref{fig:comparison}(c) shows that the assumption of a
red-noise background with the same confidence level significantly
reduces the area for which a detection may be claimed.  This simulated
data, along with the results of Section \ref{sec:anal}, suggest that
when examining the wavelet transforms of time-series for wave packets,
a background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for alternating
brightening/darkening in those plots as a indicator of a propagating
wave.  This is essentially a coherence-based approach, as the user is
assessing the likelihood that an oscillation has been detected based
on the observed signal in multiple contiguous pixels.  However, each
pixel in these plots probably has a red-noise background power
spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
that the significance of any claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
superior description of the observed Fourier power spectrum.  This
model is consistent with previous observations by TRACE of power in
the frequency range of 1 - 10 mHz.  The moss region shows the largest
presence of this excess emission.

@@

The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
contributions from plasma at many different temperatures, heights in
the atmosphere, and many different elements \cite{}.  A deeper
understanding of the contributions from these different plasmas is
required before a good estimate of the distribution of the angle
coronal loop footpoints make with the surface can be made.

@@

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(f) = \frac{E}{1 + (2\pi f T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(f) = \sum_{T}N(T)P_{T}(f)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171} and
\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
frequency defined by the data (Section \ref{sec:obs}).

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
regions may be approximated by a normal distribution $N(\mu, \sigma)$.
The maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:sigmamean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.

The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}

@@

\bibliography{references}
\end{document}
